---
title: "Intro to RMarkdown"
author: "Jake Rozran"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: 
            smooth_scroll: true
            collapse: true
---

# How to Write `md`

Markdown is a language of it's own. Fairly straightforward - helps you style 
your document. 

## `md` "Code" 

This is plain text.  
End a line with 2 spaces to start a new paragraph.  
*italics* or _italics_  
**bold** or __bold__  
superscript^2^  
~~strikethrough~~  
[link to professor's website](www.jakelearnsdatascience.com)  
`inline code`  

```
chunk of code
another line of code
x <- 12
```

# header 1

## header 2

### header 3

#### header 4

##### header 5

---
***

> this is all a block quote. it can go on for ever. 
this is still a block quote.  

this is regular text again. 

* this is an item
* in an unordered list
    * this is subitem 1
    * this is subitem 2

1. This is an ordered list
2. This is the second item
    a. An ordered list can also have letters
    b. instead of numbers 
    
| Table header | Second header |
| ------------ | ------------- |
| item 1 | item 2 |
| item 3 | item 4 |  

# The `R` in `Rmd`

Two plus two equals `r 2 + 2`.

```{r name_of_chunk, eval = FALSE}
# We can do anything R code we want in here

4 + 4
2^3
"cat" %in% c("cat", "dog", "mouse")
```

```{r another_chunk}
library(tidyverse)
```










