---
title: "Deeper into Tableau"
subtitle: "Govern for America"  
author: "Jake Rozran"
date: "October 5, 2022"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

class: center, middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
    fig.width = 9, 
    fig.height = 3.5, 
    fig.retina = 3,
    out.width = "100%",
    cache = FALSE,
    echo = FALSE,
    message = FALSE, 
    warning = FALSE,
    hiline = TRUE
)
```

```{r xaringan-themer, include = FALSE, warning = FALSE}
library(xaringanthemer)
style_duo_accent(primary_color = "#1a3f6f", 
                 secondary_color = "#52c0ea",
                 code_font_size = "0.5rem",
                 text_font_size = "1.25rem")

# "#f24244"
```

```{r xaringan-logo, echo=FALSE}
library(xaringanExtra)

use_logo(image_url = "files/gfa_logo_clear.png",
         exclude_class = "hide_logo",
         link_url = "https://www.govern4america.org/",
         position = css_position(left = "1em", bottom = "-4em"))
```

# Welcome Back!

---

class: left, middle

# Quick Agenda

1. Review last session
    - Loading CSV (text) data
    - Calculated Fields
    - Measures vs. Dimensions
    - Measure Names as Table Headers
    - Measure Values as Table Text
    - Filters
    - Sorting Data
2. Dive into Data Visualization
    - Bar Charts & Scatter Plots
    - Colors
    - Tool Tips
    - Size
    - Creating copies of sheets

---

class: center, middle

# LET'S GRAB OUR DATA!

Same data as before. I'll pop it into the Zoom chat. 

---

class: center, middle

# Review of last session.

Let's recreate our table from last time. It will feel better to do it with some 
previous experience.

---

class: left, middle

# Steps to Create a table

1. Load the data into Tableau
2. Create calculated fields for:
    - Average Population
    - Median Population
    - Minimum Population
    - Maximum Population
    - Lower Quartile of Population (25th Percentile)
    - Upper Quartile of Population (75th Percentile)
3. Add Zip Code, City, and State to rows
4. Add Measure Names to Columns
5. Filter Measure Names for the values we've created already
6. Add Measure Values as text to populate table
7. Move columns into their logical order
8. Filter on a few zip codes

---

class: center, middle

# Create a New Table Together!

## How can we get the total 2016 population for each state?

---

class: center, middle

# Create ANOTHER New Table Together!

## Can we transform the last table to show us the total US Population in 2016?

---

class: center, middle

# Let's pivot to data visualization

## Plot Twist: It is actually WAY EASIER to create data viz than tables in Tableau... 

Plot one: Can we see how the US population has changed over the years?

What type of plot may show that best?

---

class: left, middle

# Plot One

1. Create a Line Chart
2. Change the axis to not include zero
3. Copy sheet and change it to a bar chart
4. Change the axis TO include zero
5. Change measure from continuous to discrete
6. Copy sheet and include state as a color
7. Sort state by population

---

class: center, middle

# I'm Curious, though... in 2016, what was the breakdown of zip code population?

Does anyone know any one-dimensional data graphics?

---

class: left, middle

# Plot Two

1. Add column as a row and select Histogram
2. Add a filter for 2016
3. Explain the distribution
4. Change y axis to logarithmic

---

class: center, middle

# Last for Today

Can you create a line chart of three zipcodes that are interesting to you? 
Show how the population has changed over time. 

