---
title: "Intro to RMarkdown"
author: "Jake Rozran"
date: "2022-11-16"
output: 
    html_document:
        toc: true
        toc_float: 
            smooth_scroll: true
            collapsed: true
---

# How to Write `md`

Markdown is a language of its own - it is straightforward once you get it, but 
it does have some quirks.

## `md` "Code"

This is plain text. If you want to show a new line, you need to end the line 
with two spaces.  

To have a "return character," you need two spaces at the end.  

*italics* or _italics_  
**bold** or __bold__  
superscript^2^  
~~strikethrough~~  
[link](www.govern4america.org)  
`this_will_appear_as_inline_code`

```
this = "is code"
# here is a comment in my code
```
# Header 1

## Header 2

### Header 3

#### Header 4

***

> This is a block quote

- unordered list
- second item
    - this is a sub item
    - this is a second sub item
- third item

1. Here is an ordered list
2. With a second item
    + sub-item
    + another sub item

| Table 1 | Table col 2 |
|---------|-------------|
| cell 1 | cell 2 |
| cell 3 | cell 4 is longer this time |

# The `R` in `Rmd`

We can add `R` code both inline, in this test, and in chunk (mostly how I use 
`Rmd`).

## Inline `R` Code

You write your code in line by using a tick (`) followed by an r and your code, 
closed by a last tick.

2 + 2 equals `r 2 + 2`.

## Embedded `R` Code Chunks

```{r name_of_chunk}
# Here we can run R code

4 + 4
2^3
"cat" %in% c("cat", "dog", "mouse")
```

```{r plot_chunk, echo = FALSE, out.width = "100%"}
hist(rnorm(1000))
```





